---
title: "R Notebook"
output: html_notebook
---

#Load required packages
```{r}
#General for manipulating files
library(ggplot2)
library(dplyr)
library(sf)
sf_use_s2(FALSE) 
library(devtools)
library(usethis)

#For analysis of geolocator data
devtools::install_github("SLisovski/GeoLocTools")
library(GeoLocTools)

#I think these are automatically installed with GeoLocTools (above)
devtools::install_github("SLisovski/GeoLight")
library(GeoLight)
library(BAStag)
library(SGAT)
devtools::install_github("SLisovski/TwGeos")
library(TwGeos)
devtools::install_github("benjamin-merkel/probGLS")
library(probGLS)

setupGeolocation()
```


#Import the .lux files (use drift adjusted where possible)
```{r}
SSIN_872 <- luxTrans("CB872_11May22_081102driftadj.lux") 
SSIN_878 <- luxTrans("CB878_11May22_082526driftadj.lux") 
SSIN_874 <- luxTrans("CB874_20May22_034702driftadj.lux")
SSIN_884 <- luxTrans("CB884_24May22_014703driftadj.lux") 
SSIN_880 <- luxTrans("CB880_31May22_012458driftadj.lux")
SSIN_876 <- luxTrans("CB876_05Jun22_224306driftadj.lux")
SSIN_867 <- luxTrans("CB867_15Jul22_054342driftadj.lux")
SSIN_875 <- luxTrans("CB875_21Sep22_185524.lux")

str(SSIN_867)

#It looks like this shouldn't be needed, as the files are automatically in POSIXct format when imported above
SSIN_872$datetime <- as.POSIXct(strptime(SSIN_872$datetime, format = "%Y-%m-%d %H:%M:%S", tz = "GMT"))
SSIN_878$datetime <- as.POSIXct(strptime(SSIN_878$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_874$datetime <- as.POSIXct(strptime(SSIN_874$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_884$datetime <- as.POSIXct(strptime(SSIN_884$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_880$datetime <- as.POSIXct(strptime(SSIN_880$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_876$datetime <- as.POSIXct(strptime(SSIN_876$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_867$datetime <- as.POSIXct(strptime(SSIN_867$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_875$datetime <- as.POSIXct(strptime(SSIN_875$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))

```


```{r}
SSIN_867_transitions<- twilightCalc(SSIN_867$datetime, SSIN_867$light, LightThreshold=5,ask=TRUE)
SSIN_872_transitions<- twilightCalc(SSIN_872$datetime, SSIN_872$light, LightThreshold=5,ask=TRUE)
SSIN_874_transitions<- twilightCalc(SSIN_874$datetime, SSIN_874$light, LightThreshold=5,ask=TRUE)
SSIN_875_transitions<- twilightCalc(SSIN_875$datetime, SSIN_875$light, LightThreshold=5,ask=TRUE)
SSIN_876_transitions<- twilightCalc(SSIN_876$datetime, SSIN_876$light, LightThreshold=5,ask=TRUE)
SSIN_878_transitions<- twilightCalc(SSIN_878$datetime, SSIN_878$light, LightThreshold=5,ask=TRUE)
SSIN_880_transitions<- twilightCalc(SSIN_880$datetime, SSIN_880$light, LightThreshold=5,ask=TRUE)
SSIN_884_transitions<- twilightCalc(SSIN_884$datetime, SSIN_884$light, LightThreshold=5,ask=TRUE)


subset(SSIN_875_transitions, tFirst > as.POSIXct("2021-05-22") & tFirst < as.POSIXct("2021-05-25"))
SSIN_875_transitions <- SSIN_875_transitions[-c(13:15),]
SSIN_875_transitions <- SSIN_875_transitions[-c(31:32),]
SSIN_875_transitions <- SSIN_875_transitions[-c(317:319),]
SSIN_875_transitions <- SSIN_875_transitions[-c(709:716),] #This removes records at the end when the tag malfunctioned

subset(SSIN_867_transitions, tFirst > as.POSIXct("2021-07-22") & tFirst < as.POSIXct("2021-07-26"))
SSIN_867_transitions <- SSIN_867_transitions[-c(127:129),]
SSIN_867_transitions <- SSIN_867_transitions[-c(209:211),]

write.csv(SSIN_867_transitions, "SSIN_867_transitions.csv")
write.csv(SSIN_875_transitions, "SSIN_875_transitions.csv")



```


```{r}
# set threshold #
threshold <- 2.5
# Create a list to hold the transition data #
twl<-vector('list',length(SSIN_867))

# Here we define the transitions #
# NOTE - this is an interactive processes !
# Two plot windows will open for each bird (even in a loop it goes through one ind at a time #
# The two plot windows may open on top on one another - be sure to move them so you can see both#
# The process takes 4 steps - pressing "a" moves you to the next step 
# Step 1) Determine the range of dates to find twilights 
#          Plot heading = "Select Subset"
#          The current selection is shown as a red bar over the plot
#         1) To change the selection - left click on the start date and right click on the end date
#            press "a"
# Step 2) Determine a few transitions so that the whole file can be done 'automatically' 
#          Plot heading = "Find Twilights"
#         1) left click on the plot with the heading in an area that looks "decent"
#            the second plot should zoom to that area
#         2) click on the night (white) portion of the figure for both sunrise and sunset 
#            where there is a nice solid black to white transition - continue to do this until
#            the transitions show up automatically - basically you are providing a "training"
#            dataset to search for transitions - once all transitions show up (Orange and Blue)
#         3) press "a"
# Step 3) Adding transitions - this is not discussed here - we will take all the ones that were found
# Step 4) Editing transitions - this is not discussed here - we will take all the ones that were found
# IMPORTANT - press "q" to save the data to R 

for(i in 1:length(twl)){
twl[[i]] <- preprocessLight(twl[[i]], threshold, offset = offset, zlim = c(0, 12))
}
preprocessLight(SSIN_867, threshold, offset = offset, zlim = c(0, 12))


```


#Import transitions files
```{r}
import_transition <- function(transition_file) {
  transition <- read.csv (transition_file, row.names=1, header = T)
  transition$tFirst <- as.POSIXct(strptime(transition$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
  transition$tSecond <- as.POSIXct(strptime(transition$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
  
  return(transition)
}

SSIN_867_transitions <- import_transition("SSIN_867_transitions.csv")
SSIN_872_transitions <- import_transition("SSIN_872_transitions.csv")
SSIN_874_transitions <- import_transition("SSIN_874_transitions.csv")
SSIN_875_transitions <- import_transition("SSIN_875_transitions.csv")
SSIN_876_transitions <- import_transition("SSIN_876_transitions.csv")
SSIN_878_transitions <- import_transition("SSIN_878_transitions.csv")
SSIN_880_transitions <- import_transition("SSIN_880_transitions.csv")
SSIN_884_transitions <- import_transition("SSIN_884_transitions.csv")

```

#Set up function to remove uncertain locations during equinox
```{r}
equinox_remove <- function(file) {
  aut_equinox_start <- as.POSIXct("2021-09-09", format = "%Y-%m-%d",  tz = "GMT")
  aut_equinox_end <- as.POSIXct("2021-10-07", format = "%Y-%m-%d",  tz = "GMT")
  spr_equinox_start <- as.POSIXct("2022-03-06", format = "%Y-%m-%d",  tz = "GMT")
  spr_equinox_end <- as.POSIXct("2022-04-03", format = "%Y-%m-%d",  tz = "GMT")
  
  clipped <- subset(file, tFirst < aut_equinox_start | (tSecond > aut_equinox_end & tFirst < spr_equinox_start) | tSecond > spr_equinox_end)
  return(clipped)

}

SSIN_867_transitions_clip <- equinox_remove(SSIN_867_transitions)
SSIN_872_transitions_clip <- equinox_remove(SSIN_872_transitions)
SSIN_874_transitions_clip <- equinox_remove(SSIN_874_transitions)
SSIN_875_transitions_clip <- equinox_remove(SSIN_875_transitions)
SSIN_876_transitions_clip <- equinox_remove(SSIN_876_transitions)
SSIN_878_transitions_clip <- equinox_remove(SSIN_878_transitions)
SSIN_880_transitions_clip <- equinox_remove(SSIN_880_transitions)
SSIN_884_transitions_clip <- equinox_remove(SSIN_884_transitions)


```

#Introduce Loess function to remove outliers
```{r}
loess_remove <- function(file) {
  keep <- loessFilter(file,k = 1, plot = F)
  clipped <- file[keep,]
  
  return(clipped)
}

SSIN_867_transitions_clip2 <- loess_remove(SSIN_867_transitions_clip)
SSIN_872_transitions_clip2 <- loess_remove(SSIN_872_transitions_clip)
SSIN_874_transitions_clip2 <- loess_remove(SSIN_874_transitions_clip)
SSIN_875_transitions_clip2 <- loess_remove(SSIN_875_transitions_clip)
SSIN_876_transitions_clip2 <- loess_remove(SSIN_876_transitions_clip)
SSIN_878_transitions_clip2 <- loess_remove(SSIN_878_transitions_clip)
SSIN_880_transitions_clip2 <- loess_remove(SSIN_880_transitions_clip)
SSIN_884_transitions_clip2 <- loess_remove(SSIN_884_transitions_clip)

loessFilter(SSIN_867_transitions, k = 2, plot = TRUE)

```

#If we are happy with the above filters, the import and filtering can be simplified to this equation
```{r}
SSIN_867_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_867_transitions.csv")))
SSIN_872_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_872_transitions.csv")))
SSIN_874_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_874_transitions.csv")))
SSIN_875_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_875_transitions.csv")))
SSIN_876_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_876_transitions.csv")))
SSIN_878_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_878_transitions.csv")))
SSIN_880_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_880_transitions.csv")))
SSIN_884_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_884_transitions.csv")))

```


#This function calculates the sun elevation corresponding to the light level used to estimate sunrise and sunset times. 
The function allows us to calculate separately for each individual, in case of differences between tags. I am calibrating for each individual from the date of tagging until 7 July, assuming that all birds would remain on breeding grounds until this date (when nesting season is still underway)
Trying to fit this to the targeted calibration period or a shorter period (eg 2-3 weeks) seems to result in lower accuracy, and locations estimated in the South China Sea
```{r}

calibration <- function(file, tag_date) {
  start_date <- as.POSIXct(tag_date, format = "%Y-%m-%d") +(24*3600)
  calibration_date <- as.POSIXct("2021-07-07", format = "%Y-%m-%d")
  extract <- subset(file, tFirst > start_date & tSecond <= calibration_date)
  elevation <- getElevation(twl = extract, known.coord = c(114.07, 22.5), plot = TRUE, method = "gamma")
  
  return(elevation)
}

elevation_867 <- calibration(SSIN_867_transitions_clipb, "2021-06-01")
elevation_872 <- calibration(SSIN_872_transitions_clipb, "2021-06-08")
elevation_874 <- calibration(SSIN_874_transitions_clipb, "2021-05-27")
elevation_875 <- calibration(SSIN_875_transitions_clipb, "2021-05-27")
elevation_876 <- calibration(SSIN_876_transitions_clipb, "2021-05-27")
elevation_878 <- calibration(SSIN_878_transitions_clipb, "2021-05-20")
elevation_880 <- calibration(SSIN_880_transitions_clipb, "2021-06-08")
elevation_884 <- calibration(SSIN_884_transitions_clipb, "2021-06-08")

  
start_date <- as.POSIXct("2021-05-27", format = "%Y-%m-%d") + (24*3600)
calibration_date <- as.POSIXct("2021-07-07", format = "%Y-%m-%d")
extract <- subset(SSIN_875_transitions, tFirst > start_date & tSecond <= calibration_date)
elevation <- getElevation(twl = extract, known.coord = c(114.07, 22.5), plot = TRUE, method = "log-norm", lnorm.pars = TRUE)
str(elevation)


calib_867 <- subset(SSIN_867_transitions, (tFirst >= 2021-05-22 & tSecond <= 2021-01-06) | (tFirst >= 2022-07-10 & tSecond <= 2022-07-15))
elevation <- getElevation(twl = calib_867, known.coord = c(114.1401, 22.4448), plot = TRUE, method = "gamma")
elevation
str(SSIN_867_transitions)
tail(calib_867)
calib_867 <- subset(SSIN_867_transitions, (tFirst > "2021-05-22" & tSecond <= "2021-06-02") | (tFirst > "2022-07-10" & tSecond <= "2022-07-16"))

```


#Function to estimate the locations for each individual
The elevations I have used here are the median values calculated above (using data from the date of tagging until 7 July, assuming birds remain on breeding grounds until this date)
```{r}
get_location <- function(transitions_file, elevation, individual) {
 locations <- coord(transitions_file$tFirst, transitions_file$tSecond, transitions_file$type, degElevation=elevation)
 locations_df <- as.data.frame(locations)
 locations_df$Date <- as.Date.POSIXct(transitions_file$tFirst)
 locations_df$Individual <- individual
 locations_df <- locations_df[,c(4,3,1,2)]
   
 return(locations_df)
}

SSIN_867_locations2 <- get_location(SSIN_867_transitions, c(-5.123), "867")
SSIN_872_locations2 <- get_location(SSIN_872_transitions, c(-4.006), "872")
SSIN_874_locations2 <- get_location(SSIN_874_transitions, c(-4.555), "874")
SSIN_875_locations2 <- get_location(SSIN_875_transitions, c(-4.81), "875")
SSIN_876_locations2 <- get_location(SSIN_876_transitions, c(-4.96), "876")
SSIN_878_locations2 <- get_location(SSIN_878_transitions, c(-4.662), "878")
SSIN_880_locations2 <- get_location(SSIN_880_transitions, c(-4.939), "880")
SSIN_884_locations2 <- get_location(SSIN_884_transitions, c(-3.954), "884")

SSIN_867_locations3 <- get_location(SSIN_867_transitions, c(-5.079), "867")
SSIN_872_locations3 <- get_location(SSIN_872_transitions, c(-4.058), "872")
SSIN_874_locations3 <- get_location(SSIN_874_transitions, c(-4.273), "874")
SSIN_875_locations3 <- get_location(SSIN_875_transitions, c(-5.307), "875")
SSIN_876_locations3 <- get_location(SSIN_876_transitions, c(-4.72), "876")
SSIN_878_locations3 <- get_location(SSIN_878_transitions, c(-4.497), "878")
SSIN_880_locations3 <- get_location(SSIN_880_transitions, c(-4.928), "880")
SSIN_884_locations3 <- get_location(SSIN_884_transitions, c(-3.939), "884")

allbirds <- rbind(SSIN_867_locations3, SSIN_872_locations3, SSIN_874_locations3, SSIN_875_locations3, SSIN_876_locations3, SSIN_878_locations3, SSIN_880_locations3, SSIN_884_locations3)
allbirds$Individual <- as.factor(allbirds$Individual)
allbirds <- na.omit(allbirds) #remove the NAs
coordinates(allbirds) <- ~lon+lat # transform it into a SpatialPointsDataFrame to be able to assign a projection later


```



#Calculate rolling means of locations
- I've included this for 3, 5 and 10 days, we can adjust to other frequencies. 
- May help to simplify some of the results and reduce noise, but it may not be necessary
```{r}
rolling <- function(location_file) {
  rolling <- location_file %>%
  mutate(lon3day = zoo::rollmean(lon, k=3, fill=NA, align='right')) %>%
  mutate(lat3day = zoo::rollmean(lat, k=3, fill=NA, align='right')) %>%
  mutate(lon5day = zoo::rollmean(lon, k=5, fill=NA, align='right')) %>%
  mutate(lat5day = zoo::rollmean(lat, k=5, fill=NA, align='right')) %>%
  mutate(lon10day = zoo::rollmean(lon, k=10, fill=NA, align='right')) %>%
  mutate(lat10day = zoo::rollmean(lat, k=10, fill=NA, align='right'))

  return(rolling)
}

SSIN_867_rolling <- rolling(SSIN_867_locations2)
SSIN_872_rolling <- rolling(SSIN_872_locations2)
SSIN_874_rolling <- rolling(SSIN_874_locations2)
SSIN_875_rolling <- rolling(SSIN_875_locations2)
SSIN_876_rolling <- rolling(SSIN_876_locations2)
SSIN_878_rolling <- rolling(SSIN_878_locations2)
SSIN_880_rolling <- rolling(SSIN_880_locations2)
SSIN_884_rolling <- rolling(SSIN_884_locations2)

```


#Graphs showing longitude (actual and smoothed over 5 days) to estimate migration dates
Equinox periods shaded as grey
```{r}
equinox_graph <- ggplot() +
  geom_rect(aes(xmin = as.Date("2021-09-09", format = "%Y-%m-%d"), xmax = as.Date("2021-10-07", format = "%Y-%m-%d"), ymin = -Inf, ymax = Inf)) +
  geom_rect(aes(xmin = as.Date("2022-03-06", format = "%Y-%m-%d"), xmax = as.Date("2022-04-03", format = "%Y-%m-%d"), ymin = -Inf, ymax = Inf))

equinox_graph + geom_line(data = SSIN_867_rolling, aes(x = Date, y = lon5day))
equinox_graph + geom_line(data = SSIN_872_rolling, aes(x = Date, y = lon5day))
equinox_graph + geom_line(data = SSIN_874_rolling, aes(x = Date, y = lon5day))
equinox_graph + geom_line(data = SSIN_875_rolling, aes(x = Date, y = lon5day))
equinox_graph + geom_line(data = SSIN_876_rolling, aes(x = Date, y = lon5day))
equinox_graph + geom_line(data = SSIN_878_rolling, aes(x = Date, y = lon5day))
equinox_graph + geom_line(data = SSIN_880_rolling, aes(x = Date, y = lon5day))
equinox_graph + geom_line(data = SSIN_884_rolling, aes(x = Date, y = lon5day))

```

#Reaching clear estimates of migration dates, based on longitude
Includes data within the equinox periods 
```{r}
equinox_graph + geom_line(data = SSIN_867_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_867_locations2, (Date >= as.Date("2021-09-14") & Date <= as.Date("2021-09-16")))
subset(SSIN_867_locations2, (Date >= as.Date("2022-03-19") & Date <= as.Date("2022-03-21")))
#Westward movement on 15 September, eastward movement on 20 March

equinox_graph + geom_line(data = SSIN_872_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_872_locations2, (Date >= as.Date("2021-09-04") & Date <= as.Date("2021-09-07")))
subset(SSIN_872_locations2, (Date >= as.Date("2022-03-17") & Date <= as.Date("2022-03-19")))
#Eastward movement on 4 September, westward movement on 18 March

equinox_graph + geom_line(data = SSIN_874_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_874_locations2, (Date >= as.Date("2021-09-01") & Date <= as.Date("2021-09-03")))
subset(SSIN_874_locations2, (Date >= as.Date("2022-03-08") & Date <= as.Date("2022-03-10")))
#Westward movement on 02 September, eastward movement on 09 March

equinox_graph + geom_line(data = SSIN_875_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_875_locations2, (Date >= as.Date("2021-09-17") & Date <= as.Date("2021-09-19")))
subset(SSIN_875_locations2, (Date >= as.Date("2022-03-23") & Date <= as.Date("2022-03-27")))
#Westward movement on 18 September, eastward movement on 24-26 March

equinox_graph + geom_line(data = SSIN_876_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_876_locations2, (Date >= as.Date("2021-09-17") & Date <= as.Date("2021-09-19")))
subset(SSIN_876_locations2, (Date >= as.Date("2022-03-23") & Date <= as.Date("2022-03-26")))
#Westward movement on 18 September, eastward movement on 24-25 March

equinox_graph + geom_line(data = SSIN_878_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_878_locations2, (Date >= as.Date("2021-09-17") & Date <= as.Date("2021-09-20")))
subset(SSIN_878_locations2, (Date >= as.Date("2022-04-09") & Date <= as.Date("2022-04-13")))
#Westward movement on 18-19 September, eastward movement on 09-13 April

equinox_graph + geom_line(data = SSIN_880_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_880_locations2, (Date >= as.Date("2021-09-03") & Date <= as.Date("2021-09-11")))
subset(SSIN_880_locations2, (Date >= as.Date("2022-03-24") & Date <= as.Date("2022-03-26")))
#Westward movement on 04-10 September, eastward movement on 25 March

equinox_graph + geom_line(data = SSIN_884_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_884_locations2, (Date >= as.Date("2021-09-02") & Date <= as.Date("2021-09-06")))
subset(SSIN_884_locations2, (Date >= as.Date("2022-03-21") & Date <= as.Date("2022-03-26")))
#Westward movement on 03-06 September, eastward movement on 22-25 March

equinox_graph + geom_line(data = SSIN_867_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
equinox_graph + geom_line(data = SSIN_872_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
equinox_graph + geom_line(data = SSIN_874_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
equinox_graph + geom_line(data = SSIN_875_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
equinox_graph + geom_line(data = SSIN_876_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
equinox_graph + geom_line(data = SSIN_878_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
equinox_graph + geom_line(data = SSIN_880_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
equinox_graph + geom_line(data = SSIN_884_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))


equinox_graph + geom_line(data = SSIN_867_locations2, aes(x = Date, y = lat)) 
equinox_graph + geom_line(data = SSIN_872_locations2, aes(x = Date, y = lat)) 
equinox_graph + geom_line(data = SSIN_874_locations2, aes(x = Date, y = lat)) 
equinox_graph + geom_line(data = SSIN_875_locations2, aes(x = Date, y = lat)) 
equinox_graph + geom_line(data = SSIN_876_locations2, aes(x = Date, y = lat)) 
equinox_graph + geom_line(data = SSIN_878_locations2, aes(x = Date, y = lat)) 
equinox_graph + geom_line(data = SSIN_880_locations2, aes(x = Date, y = lat)) 
equinox_graph + geom_line(data = SSIN_884_locations2, aes(x = Date, y = lat)) 


```


#Sets up a background map cropped to approriate area to use for creating maps
```{r}
worldmap <- rnaturalearth::ne_countries(scale="medium", returnclass="sf")     
background_map <- ggplot() + 
  geom_sf(data = worldmap, fill="grey30", lwd=0.1, projection=st_crs("+proj=longlat +datum=WGS84"))+         
  coord_sf(xlim=c(100,130), ylim=c(5,35))                                       

background_map

background_map + geom_point(data = SSIN_867_locations2, aes(x=lon, y=lat,colour="867"), size=1, shape=20)

```



```{r}
# twilight errors
alpha <- c(2.379,0.338)
# speed distribution
beta  <- c(0.7, 0.05)

opar <- par(mfrow = c(1,2))
m <- seq(0, 60, length = 80)
plot(m, dlnorm(m, alpha[1], alpha[2]), type="l", xlab = "Twilight Error (mins)", ylim = c(0, 0.2),
     lwd = 2, main="twilight error distribution")

kmh <- 1:90
plot(kmh, dgamma(kmh, beta[1], beta[2]), type = "l", col = "orange", lwd = 2,
     main="speed distribution"  )


```


```{r}
tw <- twilight_error_estimation(shape = 2.49, scale = 0.94, delay = 0)
start_date <- as.POSIXct("2021-06-01", tz = "Asia/Hong_Kong")
end_date <- as.POSIXct("2022-07-10", tz = "Asia/Hong_Kong")
lon.calib <- 114.1
lat.calib <- 22.2
act <- as.data.frame(as.POSIXct(seq(from = start_date, to = end_date, by = (3600 * 24))))
act$wetdry <- 0
colnames(act) <- c("date", "wetdry")
str(act)
pr   <- prob_algorithm(trn = SSIN_867_transitions,
                       sensor = NULL,
                       act = act,
                       tagging.date = start_date, 
                       retrieval.date = end_date, 
                       loess.quartile = NULL, 
                       tagging.location = c(lon.calib, lat.calib), 
                       particle.number = 500, 
                       iteration.number = 100, 
                       sunrise.sd = tw,
                       sunset.sd = tw,
                       range.solar = c(-7,-1),
                       boundary.box = NULL,
                       land.mask = NULL)
str(pr)
str(SSIN_867_transitions)



```







```{r}
ssin <- rbind(SSIN_867_locations2, SSIN_872_locations2, SSIN_874_locations2, SSIN_875_locations2, SSIN_876_locations2, SSIN_878_locations2, SSIN_880_locations2, SSIN_884_locations)
ssin$Individual <- as.factor(ssin$Individual)
ssin <- na.omit(ssin) #remove the NAs
coordinates(ssin) <- ~lon+lat # transform it into a SpatialPointsDataFrame to be able to assign a projection later

```

