---
title: "R Notebook"
output: html_notebook
---

#Load required packages
```{r}
library(GeoLight)
library(raster)
library(rnaturalearth)
library(ggplot2)
library(dplyr)
library(sf)
sf_use_s2(FALSE) 
library(devtools)
library(usethis)
library(processx)
library(sgat)
library(zoo)

```

#Import transitions files
```{r}
SSIN_878_transitions <- read.csv ("SSIN_878_transitions.csv", row.names=1, header = T)
SSIN_878_transitions$tFirst <- as.POSIXct(strptime(SSIN_878_transitions$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_878_transitions$tSecond <- as.POSIXct(strptime(SSIN_878_transitions$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))

SSIN_872_transitions <- read.csv ("SSIN_872_transitions.csv", row.names=1, header = T)
SSIN_872_transitions$tFirst <- as.POSIXct(strptime(SSIN_872_transitions$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_872_transitions$tSecond <- as.POSIXct(strptime(SSIN_872_transitions$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))

SSIN_874_transitions <- read.csv ("SSIN_874_transitions.csv", row.names=1, header = T)
SSIN_874_transitions$tFirst <- as.POSIXct(strptime(SSIN_874_transitions$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_874_transitions$tSecond <- as.POSIXct(strptime(SSIN_874_transitions$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))

SSIN_880_transitions <- read.csv ("SSIN_880_transitions.csv", row.names=1, header = T)
SSIN_880_transitions$tFirst <- as.POSIXct(strptime(SSIN_880_transitions$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_880_transitions$tSecond <- as.POSIXct(strptime(SSIN_880_transitions$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))

SSIN_884_transitions <- read.csv ("SSIN_884_transitions.csv", row.names=1, header = T)
SSIN_884_transitions$tFirst <- as.POSIXct(strptime(SSIN_884_transitions$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_884_transitions$tSecond <- as.POSIXct(strptime(SSIN_884_transitions$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))

SSIN_876_transitions <- read.csv ("SSIN_876_transitions.csv", row.names=1, header = T)
SSIN_876_transitions$tFirst <- as.POSIXct(strptime(SSIN_876_transitions$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_876_transitions$tSecond <- as.POSIXct(strptime(SSIN_876_transitions$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))

```

#Set up function to remove uncertain locations during equinox
```{r}
equinox_remove <- function(file) {
  aut_equinox_start <- as.POSIXct("2021-09-09", format = "%Y-%m-%d",  tz = "GMT")
  aut_equinox_end <- as.POSIXct("2021-10-07", format = "%Y-%m-%d",  tz = "GMT")
  spr_equinox_start <- as.POSIXct("2022-03-06", format = "%Y-%m-%d",  tz = "GMT")
  spr_equinox_end <- as.POSIXct("2022-04-03", format = "%Y-%m-%d",  tz = "GMT")
  
  clipped <- subset(file, tFirst < aut_equinox_start | (tSecond > aut_equinox_end & tFirst < spr_equinox_start) | tSecond > spr_equinox_end)
  return(clipped)

}

SSIN_872_transitions_clip <- equinox_remove(SSIN_872_transitions)
SSIN_874_transitions_clip <- equinox_remove(SSIN_874_transitions)
SSIN_876_transitions_clip <- equinox_remove(SSIN_876_transitions)
SSIN_878_transitions_clip <- equinox_remove(SSIN_878_transitions)
SSIN_880_transitions_clip <- equinox_remove(SSIN_880_transitions)
SSIN_884_transitions_clip <- equinox_remove(SSIN_884_transitions)


```

#Introduce Loess function to remove outliers
```{r}
loess_remove <- function(file) {
  keep <- loessFilter(file,k = 1, plot = F)
  clipped <- file[keep,]
  
  return(clipped)
}

SSIN_872_transitions_clip2 <- loess_remove(SSIN_872_transitions_clip)
SSIN_874_transitions_clip2 <- loess_remove(SSIN_874_transitions_clip)
SSIN_876_transitions_clip2 <- loess_remove(SSIN_876_transitions_clip)
SSIN_878_transitions_clip2 <- loess_remove(SSIN_878_transitions_clip)
SSIN_880_transitions_clip2 <- loess_remove(SSIN_880_transitions_clip)
SSIN_884_transitions_clip2 <- loess_remove(SSIN_884_transitions_clip)

```

# calculate the sun elevation angle. I used SSIN 880 because it is the one that worked the best.
the calibration days do not seem to work very well with the model, and so I estimated the time where the bird would be at the site at the end of the season. 
```{r}
SunElev880<-getElevation(tFirst=SSIN_880_transitions[613:730,1],
                         tSecond = SSIN_880_transitions[613:730,2],
                         type = SSIN_880_transitions[613:730,3],
                         known.coord=c(114.07,22.5),
                         plot=TRUE, method="gamma")

```


#Function to estimate the locations for each individual
```{r}
get_location <- function(file, individual) {
 locations <- coord(file$tFirst, file$tSecond, file$type, degElevation=-4.172)
 locations_df <- as.data.frame(locations)
 locations_df$Date <- as.Date.POSIXct(file$tFirst)
 locations_df$Individual <- individual
 locations_df <- locations_df[,c(4,3,1,2)]
   
 return(locations_df)
}

SSIN_872_locations <- get_location(SSIN_872_transitions_clip2, "872")
SSIN_874_locations <- get_location(SSIN_874_transitions_clip2, "874")
SSIN_876_locations <- get_location(SSIN_876_transitions_clip2, "876")
SSIN_878_locations <- get_location(SSIN_878_transitions_clip2, "878")
SSIN_880_locations <- get_location(SSIN_880_transitions_clip2, "880")
SSIN_884_locations <- get_location(SSIN_884_transitions_clip2, "884")

```

#Calculate rolling means of locations
I've included this for 3, 5 and 10 days, we can adjust to other frequencies
```{r}
rolling <- function(location_file) {
  rolling <- location_file %>%
  mutate(lon3day = rollmean(lon, k=3, fill=NA, align='right')) %>%
  mutate(lat3day = rollmean(lat, k=3, fill=NA, align='right')) %>%
  mutate(lon5day = rollmean(lon, k=5, fill=NA, align='right')) %>%
  mutate(lat5day = rollmean(lat, k=5, fill=NA, align='right')) %>%
  mutate(lon10day = rollmean(lon, k=10, fill=NA, align='right')) %>%
  mutate(lat10day = rollmean(lat, k=10, fill=NA, align='right'))

  return(rolling)
}

SSIN_872_rolling <- rolling(SSIN_872_locations)
SSIN_874_rolling <- rolling(SSIN_874_locations)
SSIN_876_rolling <- rolling(SSIN_876_locations)
SSIN_878_rolling <- rolling(SSIN_878_locations)
SSIN_880_rolling <- rolling(SSIN_880_locations)
SSIN_884_rolling <- rolling(SSIN_884_locations)

```

#Graphs showing longitude (actual and smoothed over 5 days) to estimate migration dates
```{r}
ggplot(data = SSIN_872_rolling) +
  geom_line(aes(x = Date, y = lon)) +
  geom_line(aes(x = Date, y = lon5day, colour = "red"))

```

