---
title: "R Notebook"
output: html_notebook
---

#Load required packages
```{r}

library(GeoLight)
library(raster)
library(rnaturalearth)
library(ggplot2)
library(dplyr)
library(sf)
sf_use_s2(FALSE) 
library(devtools)
library(usethis)
library(processx)
library(sgat)
library(zoo)

```


#Import the .lux files (use drift adjusted where possible)
```{r}
SSIN_872 <- luxTrans("CB872_11May22_081102driftadj.lux") 
SSIN_878 <- luxTrans("CB878_11May22_082526driftadj.lux") 
SSIN_874 <- luxTrans("CB874_20May22_034702driftadj.lux")
SSIN_884 <- luxTrans("CB884_24May22_014703driftadj.lux") 
SSIN_880 <- luxTrans("CB880_31May22_012458driftadj.lux")
SSIN_876 <- luxTrans("CB876_05Jun22_224306driftadj.lux")
SSIN_867 <- luxTrans("CB867_15Jul22_054342driftadj.lux")
SSIN_875 <- luxTrans("CB875_21Sep22_185524.lux")

SSIN_872$datetime <- as.POSIXct(strptime(SSIN_872$datetime, format = "%Y-%m-%d %H:%M:%S", tz = "GMT"))
SSIN_878$datetime <- as.POSIXct(strptime(SSIN_878$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_874$datetime <- as.POSIXct(strptime(SSIN_874$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_884$datetime <- as.POSIXct(strptime(SSIN_884$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_880$datetime <- as.POSIXct(strptime(SSIN_880$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_876$datetime <- as.POSIXct(strptime(SSIN_876$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_867$datetime <- as.POSIXct(strptime(SSIN_867$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
SSIN_875$datetime <- as.POSIXct(strptime(SSIN_875$datetime, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))


```


```{r}
SSIN_867_transitions<- twilightCalc(SSIN_867$datetime, SSIN_867$light, LightThreshold=5,ask=TRUE)
SSIN_872_transitions<- twilightCalc(SSIN_872$datetime, SSIN_872$light, LightThreshold=5,ask=TRUE)
SSIN_874_transitions<- twilightCalc(SSIN_874$datetime, SSIN_874$light, LightThreshold=5,ask=TRUE)
SSIN_875_transitions<- twilightCalc(SSIN_875$datetime, SSIN_875$light, LightThreshold=5,ask=TRUE)
SSIN_876_transitions<- twilightCalc(SSIN_876$datetime, SSIN_876$light, LightThreshold=5,ask=TRUE)
SSIN_878_transitions<- twilightCalc(SSIN_878$datetime, SSIN_878$light, LightThreshold=5,ask=TRUE)
SSIN_880_transitions<- twilightCalc(SSIN_880$datetime, SSIN_880$light, LightThreshold=5,ask=TRUE)
SSIN_884_transitions<- twilightCalc(SSIN_884$datetime, SSIN_884$light, LightThreshold=5,ask=TRUE)


subset(SSIN_875_transitions, tFirst > as.POSIXct("2021-05-22") & tFirst < as.POSIXct("2021-05-25"))
SSIN_875_transitions <- SSIN_875_transitions[-c(13:15),]
SSIN_875_transitions <- SSIN_875_transitions[-c(31:32),]
SSIN_875_transitions <- SSIN_875_transitions[-c(317:319),]
SSIN_875_transitions <- SSIN_875_transitions[-c(709:716),] #This removes records at the end when the tag malfunctioned

subset(SSIN_867_transitions, tFirst > as.POSIXct("2021-07-22") & tFirst < as.POSIXct("2021-07-26"))
SSIN_867_transitions <- SSIN_867_transitions[-c(127:129),]
SSIN_867_transitions <- SSIN_867_transitions[-c(209:211),]

write.csv(SSIN_867_transitions, "SSIN_867_transitions.csv")
write.csv(SSIN_875_transitions, "SSIN_875_transitions.csv")



```



#Import transitions files
```{r}
import_transition <- function(transition_file) {
  transition <- read.csv (transition_file, row.names=1, header = T)
  transition$tFirst <- as.POSIXct(strptime(transition$tFirst, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
  transition$tSecond <- as.POSIXct(strptime(transition$tSecond, format = "%Y-%m-%d %H:%M:%S",  tz = "GMT"))
  
  return(transition)
}

SSIN_867_transitions <- import_transition("SSIN_867_transitions.csv")
SSIN_872_transitions <- import_transition("SSIN_872_transitions.csv")
SSIN_874_transitions <- import_transition("SSIN_874_transitions.csv")
SSIN_875_transitions <- import_transition("SSIN_875_transitions.csv")
SSIN_876_transitions <- import_transition("SSIN_876_transitions.csv")
SSIN_878_transitions <- import_transition("SSIN_878_transitions.csv")
SSIN_880_transitions <- import_transition("SSIN_880_transitions.csv")
SSIN_884_transitions <- import_transition("SSIN_884_transitions.csv")

```

#Set up function to remove uncertain locations during equinox
```{r}
equinox_remove <- function(file) {
  aut_equinox_start <- as.POSIXct("2021-09-09", format = "%Y-%m-%d",  tz = "GMT")
  aut_equinox_end <- as.POSIXct("2021-10-07", format = "%Y-%m-%d",  tz = "GMT")
  spr_equinox_start <- as.POSIXct("2022-03-06", format = "%Y-%m-%d",  tz = "GMT")
  spr_equinox_end <- as.POSIXct("2022-04-03", format = "%Y-%m-%d",  tz = "GMT")
  
  clipped <- subset(file, tFirst < aut_equinox_start | (tSecond > aut_equinox_end & tFirst < spr_equinox_start) | tSecond > spr_equinox_end)
  return(clipped)

}

SSIN_867_transitions_clip <- equinox_remove(SSIN_867_transitions)
SSIN_872_transitions_clip <- equinox_remove(SSIN_872_transitions)
SSIN_874_transitions_clip <- equinox_remove(SSIN_874_transitions)
SSIN_875_transitions_clip <- equinox_remove(SSIN_875_transitions)
SSIN_876_transitions_clip <- equinox_remove(SSIN_876_transitions)
SSIN_878_transitions_clip <- equinox_remove(SSIN_878_transitions)
SSIN_880_transitions_clip <- equinox_remove(SSIN_880_transitions)
SSIN_884_transitions_clip <- equinox_remove(SSIN_884_transitions)


```

#Introduce Loess function to remove outliers
```{r}
loess_remove <- function(file) {
  keep <- loessFilter(file,k = 1, plot = F)
  clipped <- file[keep,]
  
  return(clipped)
}

SSIN_867_transitions_clip2 <- loess_remove(SSIN_867_transitions_clip)
SSIN_872_transitions_clip2 <- loess_remove(SSIN_872_transitions_clip)
SSIN_874_transitions_clip2 <- loess_remove(SSIN_874_transitions_clip)
SSIN_875_transitions_clip2 <- loess_remove(SSIN_875_transitions_clip)
SSIN_876_transitions_clip2 <- loess_remove(SSIN_876_transitions_clip)
SSIN_878_transitions_clip2 <- loess_remove(SSIN_878_transitions_clip)
SSIN_880_transitions_clip2 <- loess_remove(SSIN_880_transitions_clip)
SSIN_884_transitions_clip2 <- loess_remove(SSIN_884_transitions_clip)

```

#If we are happy with the above filters, the import and filtering can be simplified to this equation
```{r}
SSIN_867_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_867_transitions.csv")))
SSIN_872_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_872_transitions.csv")))
SSIN_874_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_874_transitions.csv")))
SSIN_875_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_875_transitions.csv")))
SSIN_876_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_876_transitions.csv")))
SSIN_878_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_878_transitions.csv")))
SSIN_880_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_880_transitions.csv")))
SSIN_884_transitions_clipb <-
  loess_remove(equinox_remove(import_transition("SSIN_884_transitions.csv")))

```


#This function calculates the sun elevation corresponding to the light level used to estimate sunrise and sunset times. 
The function allows us to calculate separately for each individual, in case of differences between tags. I am calibrating for each individual from the date of tagging until 7 July, assuming that all birds would remain on breeding grounds until this date (when nesting season is still underway)
Trying to fit this to the targeted calibration period or a shorter period (eg 2-3 weeks) seems to result in lower accuracy, and locations estimated in the South China Sea
```{r}

calibration <- function(file, tag_date) {
  start_date <- as.POSIXct(tag_date, format = "%Y-%m-%d") +(24*3600)
  calibration_date <- as.POSIXct("2021-07-07", format = "%Y-%m-%d")
  extract <- subset(file, tFirst > start_date & tSecond <= calibration_date)
  elevation <- getElevation(twl = extract, known.coord = c(114.07, 22.5), plot = TRUE, method = "gamma")
  
  return(elevation)
}

elevation_867 <- calibration(SSIN_867_transitions, "2021-06-01")
elevation_872 <- calibration(SSIN_872_transitions, "2021-06-08")
elevation_874 <- calibration(SSIN_874_transitions, "2021-05-27")
elevation_875 <- calibration(SSIN_875_transitions, "2021-05-27")
elevation_876 <- calibration(SSIN_876_transitions, "2021-05-27")
elevation_878 <- calibration(SSIN_878_transitions, "2021-05-20")
elevation_880 <- calibration(SSIN_880_transitions, "2021-06-08")
elevation_884 <- calibration(SSIN_884_transitions, "2021-06-08")




```


#Function to estimate the locations for each individual
The elevations I have used here are the median values calculated above (using data from the date of tagging until 7 July, assuming birds remain on breeding grounds until this date)
```{r}
get_location <- function(transitions_file, elevation, individual) {
 locations <- coord(transitions_file$tFirst, transitions_file$tSecond, transitions_file$type, degElevation=elevation)
 locations_df <- as.data.frame(locations)
 locations_df$Date <- as.Date.POSIXct(transitions_file$tFirst)
 locations_df$Individual <- individual
 locations_df <- locations_df[,c(4,3,1,2)]
   
 return(locations_df)
}

SSIN_867_locations2 <- get_location(SSIN_867_transitions, c(-5.123), "867")
SSIN_872_locations2 <- get_location(SSIN_872_transitions, c(-4.006), "872")
SSIN_874_locations2 <- get_location(SSIN_874_transitions, c(-4.555), "874")
SSIN_875_locations2 <- get_location(SSIN_875_transitions, c(-4.81), "875")
SSIN_876_locations2 <- get_location(SSIN_876_transitions, c(-4.96), "876")
SSIN_878_locations2 <- get_location(SSIN_878_transitions, c(-4.662), "878")
SSIN_880_locations2 <- get_location(SSIN_880_transitions, c(-4.939), "880")
SSIN_884_locations2 <- get_location(SSIN_884_transitions, c(-3.954), "884")


```


#Calculate rolling means of locations
- I've included this for 3, 5 and 10 days, we can adjust to other frequencies. 
- May help to simplify some of the results and reduce noise, but it may not be necessary
```{r}
rolling <- function(location_file) {
  rolling <- location_file %>%
  mutate(lon3day = rollmean(lon, k=3, fill=NA, align='right')) %>%
  mutate(lat3day = rollmean(lat, k=3, fill=NA, align='right')) %>%
  mutate(lon5day = rollmean(lon, k=5, fill=NA, align='right')) %>%
  mutate(lat5day = rollmean(lat, k=5, fill=NA, align='right')) %>%
  mutate(lon10day = rollmean(lon, k=10, fill=NA, align='right')) %>%
  mutate(lat10day = rollmean(lat, k=10, fill=NA, align='right'))

  return(rolling)
}

SSIN_867_rolling <- rolling(SSIN_867_locations)
SSIN_872_rolling <- rolling(SSIN_872_locations)
SSIN_874_rolling <- rolling(SSIN_874_locations)
SSIN_875_rolling <- rolling(SSIN_875_locations)
SSIN_876_rolling <- rolling(SSIN_876_locations)
SSIN_878_rolling <- rolling(SSIN_878_locations)
SSIN_880_rolling <- rolling(SSIN_880_locations)
SSIN_884_rolling <- rolling(SSIN_884_locations)

```


#Graphs showing longitude (actual and smoothed over 5 days) to estimate migration dates
Equinox periods shaded as grey
```{r}
equinox_graph <- ggplot() +
  geom_rect(aes(xmin = as.Date("2021-09-09", format = "%Y-%m-%d"), xmax = as.Date("2021-10-07", format = "%Y-%m-%d"), ymin = -Inf, ymax = Inf)) +
  geom_rect(aes(xmin = as.Date("2022-03-06", format = "%Y-%m-%d"), xmax = as.Date("2022-04-03", format = "%Y-%m-%d"), ymin = -Inf, ymax = Inf))

equinox_graph + geom_line(data = SSIN_867_rolling, aes(x = Date, y = lon))
equinox_graph + geom_line(data = SSIN_872_rolling, aes(x = Date, y = lon))
equinox_graph + geom_line(data = SSIN_874_rolling, aes(x = Date, y = lon))
equinox_graph + geom_line(data = SSIN_875_rolling, aes(x = Date, y = lon))
equinox_graph + geom_line(data = SSIN_876_rolling, aes(x = Date, y = lon))
equinox_graph + geom_line(data = SSIN_878_rolling, aes(x = Date, y = lon))
equinox_graph + geom_line(data = SSIN_880_rolling, aes(x = Date, y = lon))
equinox_graph + geom_line(data = SSIN_884_rolling, aes(x = Date, y = lon))

```

#Reaching clear estimates of migration dates, based on longitude
Includes data within the equinox periods 
```{r}
equinox_graph + geom_line(data = SSIN_867_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_867_locations2, (Date >= as.Date("2021-09-14") & Date <= as.Date("2021-09-16")))
subset(SSIN_867_locations2, (Date >= as.Date("2022-03-19") & Date <= as.Date("2022-03-21")))
#Westward movement on 15 September, eastward movement on 20 March

equinox_graph + geom_line(data = SSIN_872_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_872_locations2, (Date >= as.Date("2021-09-04") & Date <= as.Date("2021-09-07")))
subset(SSIN_872_locations2, (Date >= as.Date("2022-03-17") & Date <= as.Date("2022-03-19")))
#Eastward movement on 4 September, westward movement on 18 March

equinox_graph + geom_line(data = SSIN_874_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_874_locations2, (Date >= as.Date("2021-09-01") & Date <= as.Date("2021-09-03")))
subset(SSIN_874_locations2, (Date >= as.Date("2022-03-08") & Date <= as.Date("2022-03-10")))
#Westward movement on 02 September, eastward movement on 09 March

equinox_graph + geom_line(data = SSIN_875_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_875_locations2, (Date >= as.Date("2021-09-17") & Date <= as.Date("2021-09-19")))
subset(SSIN_875_locations2, (Date >= as.Date("2022-03-23") & Date <= as.Date("2022-03-27")))
#Westward movement on 18 September, eastward movement on 24-26 March

equinox_graph + geom_line(data = SSIN_876_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_876_locations2, (Date >= as.Date("2021-09-17") & Date <= as.Date("2021-09-19")))
subset(SSIN_876_locations2, (Date >= as.Date("2022-03-23") & Date <= as.Date("2022-03-26")))
#Westward movement on 18 September, eastward movement on 24-25 March

equinox_graph + geom_line(data = SSIN_878_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_878_locations2, (Date >= as.Date("2021-09-17") & Date <= as.Date("2021-09-20")))
subset(SSIN_878_locations2, (Date >= as.Date("2022-04-09") & Date <= as.Date("2022-04-13")))
#Westward movement on 18-19 September, eastward movement on 09-13 April

equinox_graph + geom_line(data = SSIN_880_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_880_locations2, (Date >= as.Date("2021-09-03") & Date <= as.Date("2021-09-11")))
subset(SSIN_880_locations2, (Date >= as.Date("2022-03-24") & Date <= as.Date("2022-03-26")))
#Westward movement on 04-10 September, eastward movement on 25 March

equinox_graph + geom_line(data = SSIN_884_locations2, aes(x = Date, y = lon)) + scale_y_continuous(limits = c(100, 125))
subset(SSIN_884_locations2, (Date >= as.Date("2021-09-02") & Date <= as.Date("2021-09-06")))
subset(SSIN_884_locations2, (Date >= as.Date("2022-03-21") & Date <= as.Date("2022-03-26")))
#Westward movement on 03-06 September, eastward movement on 22-25 March


```


#Sets up a background map cropped to approriate area to use for creating maps
```{r}
worldmap <- rnaturalearth::ne_countries(scale="medium", returnclass="sf")     
background_map <- ggplot() + 
  geom_sf(data = worldmap, fill="grey30", lwd=0.1, projection=st_crs("+proj=longlat +datum=WGS84"))+         
  coord_sf(xlim=c(100,130), ylim=c(5,35))                                       

background_map
```


#Creates a map with all birds, showing data points between the two equinox periods
```{r}
background_map +
  geom_point(data=subset(SSIN_867_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="867"), size=1, shape=20)+
  geom_point(data=subset(SSIN_872_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="872"), size=1, shape=20)+
  geom_point(data=subset(SSIN_874_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="874"), size=1, shape=20)+
  geom_point(data=subset(SSIN_875_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="875"), size=1, shape=20)+
  geom_point(data=subset(SSIN_876_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="876"), size=1, shape=20)+
  geom_point(data=subset(SSIN_878_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="878"), size=1, shape=20)+
  geom_point(data=subset(SSIN_880_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="880"), size=1, shape=20)+
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="884"), size=1, shape=20)


background_map +
  geom_point(data=subset(SSIN_867_locations2, Date > "2021-05-10" & Date < "2022-09-01"), aes(x=lon, y=lat,colour="867"), size=1, shape=20)

str(SSIN_878_rolling)
```

#Creates a map with all birds showing an ellipse for the period January-February (mid-winter range)
```{r}
background_map +
  stat_ellipse(data=subset(SSIN_867_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="867"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_872_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="872"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_874_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="874"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_875_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="875"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_876_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="876"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_878_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="878"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_880_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="880"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_884_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="884"), size=1, shape=20)

```


#This draws the ellipse for each month for an individual. I need to adjust how to deal with aesthetics (currently all ellipses are the same colour!)
```{r}
date_ellipse <- function(file, start_date, end_date) {
  date_ellipse <- stat_ellipse(data=subset(file, Date > start_date & Date < end_date), aes(x=lon, y=lat), size=1, shape=20)
  
  return(date_ellipse)
}  

background_map +
  date_ellipse(SSIN_884_locations2, "2021-09-01", "2021-09-30") +
  date_ellipse(SSIN_884_locations2, "2021-10-01", "2021-10-31") +
  date_ellipse(SSIN_884_locations2, "2021-11-01", "2021-11-30") +
  date_ellipse(SSIN_884_locations2, "2021-12-01", "2021-12-31") +
  date_ellipse(SSIN_884_locations2, "2022-01-01", "2022-01-31") +
  date_ellipse(SSIN_884_locations2, "2022-02-01", "2022-02-28") +
  date_ellipse(SSIN_884_locations2, "2022-03-01", "2022-03-31")


```

