---
title: "R Notebook"
output: html_notebook
---

##This process is based on instructions from the following website:
https://geolocationmanual.vogelwarte.ch/

#Load required packages
```{r}
#General for manipulating files
library(ggplot2)
library(dplyr)
library(sf)
sf_use_s2(FALSE) 
library(devtools)
library(usethis)

#For analysis of geolocator data
devtools::install_github("SLisovski/GeoLocTools")
library(GeoLocTools)

#I think these are automatically installed with GeoLocTools (above)
devtools::install_github("SLisovski/GeoLight")
library(GeoLight)
library(BAStag)
library(SGAT)
devtools::install_github("SLisovski/TwGeos")
library(TwGeos)
devtools::install_github("benjamin-merkel/probGLS")
library(probGLS)

setupGeolocation()
```


#Import the .lux files (use drift adjusted where possible)
```{r}
import.lux <- function(file) {
  df <- luxTrans(file)
  colnames(df) <- c("Date", "rawLight")
  df$Light  <- log(df$rawLight+0.0001) + abs(min(log(df$rawLight+0.0001)))
  
  return(df)
}

SSIN_872 <- import.lux("CB872_11May22_081102driftadj.lux") 
SSIN_878 <- import.lux("CB878_11May22_082526driftadj.lux") 
SSIN_874 <- import.lux("CB874_20May22_034702driftadj.lux")
SSIN_884 <- import.lux("CB884_24May22_014703driftadj.lux") 
SSIN_880 <- import.lux("CB880_31May22_012458driftadj.lux")
SSIN_876 <- import.lux("CB876_05Jun22_224306driftadj.lux")
SSIN_867 <- import.lux("CB867_15Jul22_054342driftadj.lux")
SSIN_875 <- import.lux("CB875_21Sep22_185524.lux")

str(SSIN_867)
str(SSIN_872)
str(SSIN_874)
str(SSIN_875)
str(SSIN_876)
str(SSIN_878)
str(SSIN_880)
str(SSIN_884)


```


#Set calibration locations
```{r}
lon.calib <- 114.065
lat.calib <- 22.511

```


#Show light levels and threshold for twilight detection
```{r}
threshold <- 2.5

col = colorRampPalette(c('black',"purple",'orange'))(50)[as.numeric(cut(SSIN_867[3000:5000,2],breaks = 50))]

par(mfrow = c(1, 1), mar = c(2, 2, 2, 2) )
with(SSIN_872[3000:5000,], plot(Date, Light, type = "o", pch=16,  col = col, cex = 0.5)) 
abline(h=threshold, col="orange", lty = 2, lwd = 2)

```


#Plot of light level recorded throughout deployment (with twilight times at calibration location)
```{r}
offset <- 4 # adjusts the y-axis to put night (dark shades) in the middle

lightImage(tagdata = SSIN_872, offset = offset, zlim = c(0, 12))

tsimageDeploymentLines(SSIN_872$Date, lon = lon.calib, lat = lat.calib,
                       offset = offset, lwd = 3, col = adjustcolor("orange", alpha.f = 0.5))


```


#Process light files to find twilight times (this is interactive: check instructions on the website https://geolocationmanual.vogelwarte.ch/twilight.html)
```{r}
?preprocessLight

twl <- preprocessLight(SSIN_884, 
  threshold = threshold,
  offset = offset, 
  lmax = 12,         # max. light value (12 in our data)
  gr.Device = "x11") # MacOS version (and windows)

head(twl)


```

#Save twilight transitions so the above is not needed again
```{r}
wd <- "C:/Users/johna/Documents/White-shouldered Starlings/starlings"

write.csv(twl, paste(wd, "SSIN_867_twilights.csv", sep = "/"))
write.csv(twl, paste(wd, "SSIN_872_twilights.csv", sep = "/"))
write.csv(twl, paste(wd, "SSIN_874_twilights.csv", sep = "/"))
write.csv(twl, paste(wd, "SSIN_875_twilights.csv", sep = "/"))
write.csv(twl, paste(wd, "SSIN_876_twilights.csv", sep = "/"))
write.csv(twl, paste(wd, "SSIN_878_twilights.csv", sep = "/"))
write.csv(twl, paste(wd, "SSIN_880_twilights.csv", sep = "/"))
write.csv(twl, paste(wd, "SSIN_884_twilights.csv", sep = "/"))

```

