---
title: "R Notebook"
output: html_notebook
---

```{r}
#For mapping
library(raster)
library(rnaturalearth)

library(processx)
library(zoo)

```


#Sets up a background map cropped to approriate area to use for creating maps
```{r}
worldmap <- rnaturalearth::ne_countries(scale="medium", returnclass="sf")     
background_map <- ggplot() + 
  geom_sf(data = worldmap, fill="grey30", lwd=0.1, projection=st_crs("+proj=longlat +datum=WGS84"))+         
  coord_sf(xlim=c(100,130), ylim=c(5,35))                                       

background_map

background_map + geom_point(data = SSIN_867_locations2, aes(x=lon, y=lat,colour="867"), size=1, shape=20)

```


#Creates a map with all birds, showing data points between the two equinox periods
```{r}
background_map +
  geom_point(data=subset(SSIN_867_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="867"), size=1, shape=20)+
  geom_point(data=subset(SSIN_872_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="872"), size=1, shape=20)+
  geom_point(data=subset(SSIN_874_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="874"), size=1, shape=20)+
  geom_point(data=subset(SSIN_875_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="875"), size=1, shape=20)+
  geom_point(data=subset(SSIN_876_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="876"), size=1, shape=20)+
  geom_point(data=subset(SSIN_878_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="878"), size=1, shape=20)+
  geom_point(data=subset(SSIN_880_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="880"), size=1, shape=20)+
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon, y=lat,colour="884"), size=1, shape=20)

background_map +
  geom_point(data=subset(SSIN_867_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="867"), size=1, shape=20)+
  geom_point(data=subset(SSIN_872_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="872"), size=1, shape=20)+
  geom_point(data=subset(SSIN_874_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="874"), size=1, shape=20)+
  geom_point(data=subset(SSIN_875_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="875"), size=1, shape=20)+
  geom_point(data=subset(SSIN_876_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="876"), size=1, shape=20)+
  geom_point(data=subset(SSIN_878_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="878"), size=1, shape=20)+
  geom_point(data=subset(SSIN_880_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="880"), size=1, shape=20)+
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-10-08" & Date < "2022-03-05"), aes(x=lon5day, y=lat5day,colour="884"), size=1, shape=20)

background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-06-01" & Date < "2021-06-30"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-07-01" & Date < "2021-07-31"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-08-01" & Date < "2021-08-31"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-09-01" & Date < "2021-09-30"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-10-01" & Date < "2021-10-31"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-11-01" & Date < "2021-11-30"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2021-12-01" & Date < "2021-12-31"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2022-01-01" & Date < "2022-01-31"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2022-02-01" & Date < "2022-02-28"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2022-03-01" & Date < "2022-03-31"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2022-04-01" & Date < "2022-04-30"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)
background_map +
  geom_point(data=subset(SSIN_884_rolling, Date > "2022-05-01" & Date < "2022-05-31"), aes(x=lon3day, y=lat3day,colour="884"), size=1, shape=20)

str(SSIN_878_rolling)
```

#Creates a map with all birds showing an ellipse for the period December-January (mid-winter range)
```{r}
background_map +
  stat_ellipse(data=subset(SSIN_867_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="867"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_872_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="872"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_874_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="874"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_875_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="875"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_876_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="876"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_878_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="878"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_880_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="880"), size=1, shape=20)+
  stat_ellipse(data=subset(SSIN_884_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="884"), size=1, shape=20)


background_map +
  geom_point(data=subset(SSIN_867_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="867"), size=1, shape=20)+
  geom_point(data=subset(SSIN_872_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="872"), size=1, shape=20)+
  geom_point(data=subset(SSIN_874_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="874"), size=1, shape=20)+
  geom_point(data=subset(SSIN_875_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="875"), size=1, shape=20)+
  geom_point(data=subset(SSIN_876_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="876"), size=1, shape=20)+
  geom_point(data=subset(SSIN_878_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="878"), size=1, shape=20)+
  geom_point(data=subset(SSIN_880_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="880"), size=1, shape=20)+
  geom_point(data=subset(SSIN_884_locations3, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="884"), size=1, shape=20)

background_map +
  geom_point(data=subset(SSIN_867_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="867"), size=1, shape=20)+
  geom_point(data=subset(SSIN_872_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="872"), size=1, shape=20)+
  geom_point(data=subset(SSIN_874_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="874"), size=1, shape=20)+
  geom_point(data=subset(SSIN_875_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="875"), size=1, shape=20)+
  geom_point(data=subset(SSIN_876_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="876"), size=1, shape=20)+
  geom_point(data=subset(SSIN_878_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="878"), size=1, shape=20)+
  geom_point(data=subset(SSIN_880_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="880"), size=1, shape=20)+
  geom_point(data=subset(SSIN_884_locations2, Date > "2021-12-01" & Date < "2022-01-31"), aes(x=lon, y=lat,colour="884"), size=1, shape=20)

```


#This draws the ellipse for each month for an individual. I need to adjust how to deal with aesthetics (currently all ellipses are the same colour!)
```{r}
date_ellipse <- function(file, start_date, end_date) {
  date_ellipse <- stat_ellipse(data=subset(file, Date > start_date & Date < end_date), aes(x=lon, y=lat), size=1, shape=20)
  
  return(date_ellipse)
}  

background_map +
  date_ellipse(SSIN_884_locations2, "2021-09-01", "2021-09-30") +
  date_ellipse(SSIN_884_locations2, "2021-10-01", "2021-10-31") +
  date_ellipse(SSIN_884_locations2, "2021-11-01", "2021-11-30") +
  date_ellipse(SSIN_884_locations2, "2021-12-01", "2021-12-31") +
  date_ellipse(SSIN_884_locations2, "2022-01-01", "2022-01-31") +
  date_ellipse(SSIN_884_locations2, "2022-02-01", "2022-02-28") +
  date_ellipse(SSIN_884_locations2, "2022-03-01", "2022-03-31")


```

