---
title: "R Notebook"
output: html_notebook
---


#Read in data and convert to correct format
```{r}
lon.calib <- 114.065
lat.calib <- 22.511

wd <- "C:/Users/johna/Documents/White-shouldered Starlings/starlings"

# Read in raw data files of light intensity
SSIN_867 <- import.lux("CB867_15Jul22_054342driftadj.lux")
SSIN_872 <- import.lux("CB872_11May22_081102driftadj.lux") 
SSIN_874 <- import.lux("CB874_20May22_034702driftadj.lux")
SSIN_875 <- import.lux("CB875_21Sep22_185524.lux")
SSIN_876 <- import.lux("CB876_05Jun22_224306driftadj.lux")
SSIN_878 <- import.lux("CB878_11May22_082526driftadj.lux") 
SSIN_880 <- import.lux("CB880_31May22_012458driftadj.lux")
SSIN_884 <- import.lux("CB884_24May22_014703driftadj.lux") 

# Read in twilight time files
SSIN867_twl <- read.csv(paste(wd, "SSIN_867_twilights.csv", sep = "/"))
SSIN872_twl <- read.csv(paste(wd, "SSIN_872_twilights.csv", sep = "/"))
SSIN874_twl <- read.csv(paste(wd, "SSIN_874_twilights.csv", sep = "/"))
SSIN875_twl <- read.csv(paste(wd, "SSIN_875_twilights.csv", sep = "/"))
SSIN876_twl <- read.csv(paste(wd, "SSIN_876_twilights.csv", sep = "/"))
SSIN878_twl <- read.csv(paste(wd, "SSIN_878_twilights.csv", sep = "/"))
SSIN880_twl <- read.csv(paste(wd, "SSIN_880_twilights.csv", sep = "/"))
SSIN884_twl <- read.csv(paste(wd, "SSIN_884_twilights.csv", sep = "/"))

```



#Set up data files for the relevant individual
```{r}
raw <- SSIN_878

twl <- SSIN878_twl
twl$Twilight <- as.POSIXct(twl$Twilight, tz = "UTC")
twl <- twl[!twl$Deleted,]

raw <- subset(raw, Date>=min(twl$Twilight) & Date<=max(twl$Twilight)) # clipping raw data to relevant extent  

calibdate <- SSIN878_calibdate

#Remove equinox dates
twl <- subset(twl, Twilight <= as.POSIXct("2021-09-08") | Twilight >= as.POSIXct("2021-10-08") & Twilight <= as.POSIXct("2022-03-05") | Twilight >= as.POSIXct("2022-04-04"))

```


#FOR FEMALES ONLY - Optional to remove periods of incubation
```{r}
##For 872, 875, 876, 878
#twl <- subset(twl, Twilight < calibdate$ex1[1] | Twilight > calibdate$ex1[2])

##For 872, 875, 876, 878, 880
#twl <- subset(twl, Twilight < calibdate$ex2[1] | Twilight > calibdate$ex2[2])

##For 876
#twl <- subset(twl, Twilight < calibdate$ex3[1] | Twilight > calibdate$ex3[2])


```



#View light levels over the course of the whole year
```{r}
offset <- 4 # adjusts the y-axis to put night (dark shades) in the middle

lightImage( tagdata = raw,
            offset = offset,     
            zlim = c(0, 10))

tsimagePoints(twl$Twilight, offset = offset, pch = 16, cex = 1.2,
              col = ifelse(twl$Rise, "firebrick", "cornflowerblue"))

```


#Obtain target dates for calibration
Will need to update dates for each individual based on trapping dates and nesting dates of females: therefore this is not quite the same as on the vogelwarte website
```{r}
lightImage( tagdata = raw,
            offset = offset,     
            zlim = c(0, 10))

tsimageDeploymentLines(twl$Twilight, lon.calib, lat.calib, offset, lwd = 2, col = "orange")

tm.calib <- as.POSIXct(c("2015-07-20", "2015-08-29"), tz = "UTC")
abline(v = tm.calib, lwd = 2, lty = 2, col = "orange")


tm1 <- c(as.POSIXct("2021-05-27"), as.POSIXct("2021-07-19")) #dates present in 2021
tm2 <- c(as.POSIXct("2022-04-04"), as.POSIXct("2022-06-02")) #dates present in 2022
tm3 <- c(as.POSIXct("2021-07-05"), as.POSIXct("2021-07-19")) #exclusion period 1
tm4 <- c(as.POSIXct("2022-04-18"), as.POSIXct("2022-05-03")) #exclusion period 2
tm5 <- c(as.POSIXct("2022-05-20"), as.POSIXct("2022-06-02")) #exclusion period 3

abline(v = tm1, lty = c(1,2), col = "firebrick", lwd = 1.5)
abline(v = tm2, lty = c(1,2), col = "firebrick", lwd = 1.5)
abline(v = tm3, lty = c(1,2), col = "cornflowerblue", lwd = 1.5)
abline(v = tm4, lty = c(1,2), col = "cornflowerblue", lwd = 1.5)
abline(v = tm5, lty = c(1,2), col = "cornflowerblue", lwd = 1.5)


d_calib <- subset(twl, Twilight >= tm1[1] & Twilight <= tm1[2] | Twilight >= tm2[1] & Twilight <= tm2[2])
d_calib <- subset(d_calib, Twilight <= tm3[1] | (Twilight >= tm3[2] & Twilight <= tm4[1]) | (Twilight >= tm4[2] & Twilight <= tm5[1]) | Twilight >= tm5[2])


```


#Calibrate the twilight to estimate the sun zenith and error distribution of twilight times
Note: this is not quite the same as in the calibration sheet: uses raw twilight times, not in geoLight format
```{r}
calib <- thresholdCalibration(d_calib$Twilight, d_calib$Rise, lon.calib, lat.calib, method = "gamma")

zenith  <- calib[1]
zenith0 <- calib[2]

alpha <- calib[3:4]

```


#Set movement model (may need to adjust first beta value: low = slow movement, high = faster)
```{r}
beta  <- c(0.01, 0.08)
matplot(0:100, dgamma(0:100, beta[1], beta[2]),
        type = "l", col = "orange",lty = 1,lwd = 2,ylab = "Density", xlab = "km/h")

```


#Initial estimate of locations
```{r}
path <- thresholdPath(twl$Twilight, twl$Rise, zenith = zenith, tol=0.01)

x0 <- path$x
z0 <- trackMidpts(x0)

data(wrld_simpl)
plot(x0, type = "n", xlab = "", ylab = "", xlim = c(100,130), ylim = c(5,35))
plot(wrld_simpl, col = "grey95", add = T)

points(path$x, pch=19, col="cornflowerblue", type = "o")
points(lon.calib, lat.calib, pch = 16, cex = 2.5, col = "firebrick")
box()

```


#Define known locations
Maybe worth doing this with all dates known to be at breeding site
```{r}
fixedx <- rep(FALSE, nrow(x0))

fixedx[which(path$time <= "2021-07-19")] <- TRUE   # mark all records before 2021-07-19 as at capture site
fixedx[which(path$time >= "2022-04-04")] <- TRUE   # mark all records after 2022-04-04 as at capture site

x0[fixedx, 1] <- lon.calib
x0[fixedx, 2] <- lat.calib

z0 <- trackMidpts(x0) # we need to update the z0 locations


```


```{r}
distribution.mask <- function(xlim, ylim, n = 4, land = TRUE, shape) {
    r <- raster(nrows = n * diff(ylim), ncols = n * diff(xlim), xmn = xlim[1], 
        xmx = xlim[2], ymn = ylim[1], ymx = ylim[2], crs = proj4string(shape))
    r <- cover(rasterize(elide(shape, shift = c(-360, 0)), r, 1, silent = TRUE), 
        rasterize(shape, r, 1, silent = TRUE), rasterize(elide(shape, 
            shift = c(360, 0)), r, 1, silent = TRUE))
    r <- as.matrix(is.na(r))[nrow(r):1, ]
    if (land) 
        r <- !r
    xbin <- seq(xlim[1], xlim[2], length = ncol(r) + 1)
    ybin <- seq(ylim[1], ylim[2], length = nrow(r) + 1)

    function(p) {
        r[cbind(.bincode(p[, 2], ybin), .bincode(p[, 1], xbin))]
    }
}

xlim <- c(100, 130)
ylim <- c(0, 35)

is.dist <- distribution.mask(shape = wrld_simpl, xlim = xlim, ylim = ylim, n = 4, land = TRUE)

## Define the log prior for x and z
log.prior <- function(p) {
    f <- is.dist(p)
    ifelse(f | is.na(f), 0, -10)
}


```

#Set up land-sea mask
```{r}
earthseaMask <- function(xlim, ylim, n = 2, pacific=FALSE) {
  
  if (pacific) {wrld_simpl <- nowrapRecenter(wrld_simpl, avoidGEOS = TRUE)}
  
  # create empty raster with desired resolution
  r = raster(nrows = n * diff(ylim), ncols = n * diff(xlim), xmn = xlim[1],
              xmx = xlim[2], ymn = ylim[1], ymx = ylim[2], crs = proj4string(wrld_simpl))
  
  # create a raster for the stationary period, in this case by giving land a value of 1 and sea NA
  mask = cover(rasterize(elide(wrld_simpl, shift = c(-360, 0)), r, 1, silent = TRUE),
              rasterize(wrld_simpl, r, 1, silent = TRUE), 
              rasterize(elide(wrld_simpl,shift = c(360, 0)), r, 1, silent = TRUE))
  
  xbin = seq(xmin(mask),xmax(mask),length=ncol(mask)+1)
  ybin = seq(ymin(mask),ymax(mask),length=nrow(mask)+1)

  function(p) mask[cbind(.bincode(p[,2],ybin),.bincode(p[,1],xbin))]
}


xlim <- c(100, 130)
ylim <- c(5, 35)


mask <- earthseaMask(xlim, ylim, n = 1)

## Define the log prior for x and z
log.prior <- function(p) {
    f <- mask(p)
    ifelse(f | is.na(f), log(2), log(1))
}

```


#Fitting the estelle model
```{r}
model <- thresholdModel(twilight = twl$Twilight,
                        rise = twl$Rise,
                        twilight.model = "ModifiedGamma",
                        alpha = alpha,
                        beta = beta,
                        logp.x = log.prior, logp.z = log.prior, 
                        x0 = x0,
                        z0 = z0,
                        zenith = zenith0,
                        fixedx = fixedx)

proposal.x <- mvnorm(S=diag(c(0.0025,0.0025)),n=nlocation(x0))
proposal.z <- mvnorm(S=diag(c(0.0025,0.0025)),n=nlocation(z0))

fit <- estelleMetropolis(model, proposal.x, proposal.z, iters = 1000, thin = 20)

```



```{r}
x0 <- chainLast(fit$x)
z0 <- chainLast(fit$z)

model <- thresholdModel(twilight = twl$Twilight,
                        rise = twl$Rise,
                        twilight.model = "Gamma",
                        alpha = alpha,
                        beta = beta,
                        logp.x = log.prior, logp.z = log.prior, 
                        x0 = x0,
                        z0 = z0,
                        zenith = zenith0,
                        fixedx = fixedx)

x.proposal <- mvnorm(S = diag(c(0.0025, 0.0025)), n = nrow(twl))
z.proposal <- mvnorm(S = diag(c(0.0025, 0.0025)), n = nrow(twl) - 1)

#Refine the proposal distributions
for (k in 1:3) {
    fit <- estelleMetropolis(model, x.proposal, z.proposal, x0 = chainLast(fit$x), 
        z0 = chainLast(fit$z), iters = 300, thin = 20)
    
    x.proposal <- mvnorm(chainCov(fit$x), s = 0.2)
    z.proposal <- mvnorm(chainCov(fit$z), s = 0.2)
}


#Check the chains converge
opar <- par(mfrow = c(2, 1), mar = c(3, 5, 2, 1) + 0.1)
matplot(t(fit$x[[1]][!fixedx, 1, ]), type = "l", lty = 1, col = "dodgerblue", ylab = "Lon")
matplot(t(fit$x[[1]][!fixedx, 2, ]), type = "l", lty = 1, col = "firebrick", ylab = "Lat")
par(opar)

#Refit model using refined parameters
x.proposal <- mvnorm(chainCov(fit$x), s = 0.25)
z.proposal <- mvnorm(chainCov(fit$z), s = 0.25)

fit <- estelleMetropolis(model, x.proposal, z.proposal, x0 = chainLast(fit$x), 
                         z0 = chainLast(fit$z), iters = 1000, thin = 20)

```



```{r}
sm <- locationSummary(fit$z, time=fit$model$time)

# empty raster of the extent
r <- raster(nrows = 2 * diff(ylim), ncols = 2 * diff(xlim), xmn = xlim[1]-5,
            xmx = xlim[2]+5, ymn = ylim[1]-5, ymx = ylim[2]+5, crs = proj4string(wrld_simpl))

s <- slices(type = "intermediate", breaks = "week", mcmc = fit, grid = r)
sk <- SGAT::slice(s, sliceIndices(s))

plot(sk, useRaster = F, col = rev(viridis::viridis(50)))
plot(wrld_simpl, xlim = c(100,130), ylim = c(5,35), add = T, bg = adjustcolor("black",alpha=0.1))

lines(sm[,"Lon.50%"], sm[,"Lat.50%"], col = adjustcolor("firebrick", alpha.f = 0.6), type = "o", pch = 16, lwd = 0.5, cex = 0.5)

title(main = "Female 878", cex.main = 1, adj = 0.05, line = -1)


```



```{r}
par(mfrow=c(2,1),mar=c(4,4,1,1))
plot(sm$Time1, sm$"Lon.50%", ylab = "Longitude", xlab = "", yaxt = "n", type = "n", ylim = c(100, 130))
axis(2, las = 2)
polygon(x=c(sm$Time1,rev(sm$Time1)), y=c(sm$`Lon.2.5%`,rev(sm$`Lon.97.5%`)), border="gray", col="gray")
lines(sm$Time1,sm$"Lon.50%", lwd = 2)

plot(sm$Time1,sm$"Lat.50%", type="n", ylab = "Latitude", xlab = "", yaxt = "n", ylim = c(5,35))
axis(2, las = 2)
polygon(x=c(sm$Time1,rev(sm$Time1)), y=c(sm$`Lat.2.5%`,rev(sm$`Lat.97.5%`)), border="gray", col="gray")
lines(sm$Time1,sm$"Lat.50%", lwd = 2)
```


#Save the results
```{r}
write.csv(sm, 
          paste0(wd, "SSIN876_SGATSummary.csv"), 
          row.names = F)

save(fit, 
     file = paste0(wd, "SSIN876_SGATfit.Rdata"), 
     compress = T)
```

