---
title: "R Notebook"
output: html_notebook
---


#Read in data and convert to correct format
```{r}
lon.calib <- 114.065
lat.calib <- 22.511

wd <- "C:/Users/johna/Documents/White-shouldered Starlings/starlings"

# Read in raw data files of light intensity
SSIN_867 <- import.lux("CB867_15Jul22_054342driftadj.lux")
SSIN_872 <- import.lux("CB872_11May22_081102driftadj.lux") 
SSIN_874 <- import.lux("CB874_20May22_034702driftadj.lux")
SSIN_875 <- import.lux("CB875_21Sep22_185524.lux")
SSIN_876 <- import.lux("CB876_05Jun22_224306driftadj.lux")
SSIN_878 <- import.lux("CB878_11May22_082526driftadj.lux") 
SSIN_880 <- import.lux("CB880_31May22_012458driftadj.lux")
SSIN_884 <- import.lux("CB884_24May22_014703driftadj.lux") 

# Read in twilight time files
SSIN867_twl <- read.csv(paste(wd, "SSIN_867_twilights.csv", sep = "/"))
SSIN872_twl <- read.csv(paste(wd, "SSIN_872_twilights.csv", sep = "/"))
SSIN874_twl <- read.csv(paste(wd, "SSIN_874_twilights.csv", sep = "/"))
SSIN875_twl <- read.csv(paste(wd, "SSIN_875_twilights.csv", sep = "/"))
SSIN876_twl <- read.csv(paste(wd, "SSIN_876_twilights.csv", sep = "/"))
SSIN878_twl <- read.csv(paste(wd, "SSIN_878_twilights.csv", sep = "/"))
SSIN880_twl <- read.csv(paste(wd, "SSIN_880_twilights.csv", sep = "/"))
SSIN884_twl <- read.csv(paste(wd, "SSIN_884_twilights.csv", sep = "/"))

raw <- SSIN_876

twl <- SSIN876_twl
  twl$Twilight <- as.POSIXct(twl$Twilight, tz = "UTC")
  twl <- twl[!twl$Deleted,]

raw <- subset(raw, Date>=min(twl$Twilight) & Date<=max(twl$Twilight)) # clipping raw data to relevant extent  

```




#View light levels over the course of the whole year
```{r}
offset <- 4 # adjusts the y-axis to put night (dark shades) in the middle

lightImage( tagdata = raw,
            offset = offset,     
            zlim = c(0, 10))

tsimagePoints(twl$Twilight, offset = offset, pch = 16, cex = 1.2,
              col = ifelse(twl$Rise, "firebrick", "cornflowerblue"))

```


#Obtain target dates for calibration
Will need to update dates for each individual based on trapping dates and nesting dates of females: therefore this is not quite the same as on the vogelwarte website
```{r}
lightImage( tagdata = raw,
            offset = offset,     
            zlim = c(0, 10))

tsimageDeploymentLines(twl$Twilight, lon.calib, lat.calib, offset, lwd = 2, col = "orange")

tm.calib <- as.POSIXct(c("2015-07-20", "2015-08-29"), tz = "UTC")
abline(v = tm.calib, lwd = 2, lty = 2, col = "orange")


tm1 <- c(as.POSIXct("2021-05-27"), as.POSIXct("2021-07-19")) #dates present in 2021
tm2 <- c(as.POSIXct("2022-04-04"), as.POSIXct("2022-06-02")) #dates present in 2022
ex3 <- c(as.POSIXct("2021-07-05"), as.POSIXct("2021-07-19")) #exclusion period 1
ex4 <- c(as.POSIXct("2022-04-18"), as.POSIXct("2022-05-03")) #exclusion period 2
ex5 <- c(as.POSIXct("2022-05-20"), as.POSIXct("2022-06-02")) #exclusion period 3

abline(v = tm1, lty = c(1,2), col = "firebrick", lwd = 1.5)
abline(v = tm2, lty = c(1,2), col = "firebrick", lwd = 1.5)
abline(v = tm3, lty = c(1,2), col = "cornflowerblue", lwd = 1.5)
abline(v = tm4, lty = c(1,2), col = "cornflowerblue", lwd = 1.5)
abline(v = tm5, lty = c(1,2), col = "cornflowerblue", lwd = 1.5)


d_calib <- subset(twl, Twilight >= tm1[1] & Twilight <= tm1[2] | Twilight >= tm2[1] & Twilight <= tm2[2])
d_calib <- subset(d_calib, Twilight <= ex3[1] | (Twilight >= ex3[2] & Twilight <= ex4[1]) | (Twilight >= ex4[2] & Twilight <= ex5[1]) | Twilight >= ex5[2])


```


#Calibrate the twilight to estimate the sun zenith and error distribution of twilight times
Note: this is not quite the same as in the calibration sheet: uses raw twilight times, not in geoLight format
```{r}
calib <- thresholdCalibration(d_calib$Twilight, d_calib$Rise, lon.calib, lat.calib, method = "gamma")

zenith  <- calib[1]
zenith0 <- calib[2]

alpha <- calib[3:4]

```




#Set movement model (may need to adjust first beta value: low = slow movement, high = faster)
```{r}
beta  <- c(1, 0.08)
matplot(0:100, dgamma(0:100, beta[1], beta[2]),
        type = "l", col = "orange",lty = 1,lwd = 2,ylab = "Density", xlab = "km/h")

```


#Initial estimate of locations
```{r}
path <- thresholdPath(twl$Twilight, twl$Rise, zenith = zenith, tol=0.01)

x0 <- path$x
z0 <- trackMidpts(x0)

data(wrld_simpl)
plot(x0, type = "n", xlab = "", ylab = "", xlim = c(100,130), ylim = c(5,35))
plot(wrld_simpl, col = "grey95", add = T)

points(path$x, pch=19, col="cornflowerblue", type = "o")
points(lon.calib, lat.calib, pch = 16, cex = 2.5, col = "firebrick")
box()

```



#Define known locations
Maybe worth doing this with all dates known to be at breeding site
```{r}
fixedx <- rep(F, nrow(x0))

which(path$time > "2021-07-19")
fixedx[1:106] <- T   # mark all records before 2021-07-19 as at capture site

which(path$time > "2022-04-04")
fixedx[624:nrow(x0)] <- T   # mark all records after 2022-04-04 as at capture site

x0[fixedx, 1] <- lon.calib
x0[fixedx, 2] <- lat.calib

z0 <- trackMidpts(x0) # we need to update the z0 locations

x0

```





####THIS IS THE PART I"VE USED PREVIOUSLY


```{r}

geo_twl <- export2GeoLight(twl)

# Often it is necessary to play around with quantile and days
# quantile defines how many stopovers there are. the higher, the fewer there are
# days indicates the duration of the stopovers 
cL <- changeLight(twl=geo_twl, quantile=0.9, summary = F, days = 2, plot = T)

# merge site helps to put sites together that are separated by single outliers.
mS <- mergeSites(twl = geo_twl, site = cL$site, degElevation = 90-zenith, distThreshold = 200)


```



```{r}
twl.rev <- data.frame(Twilight = as.POSIXct(geo_twl[,1], geo_twl[,2], tz = "UTC"), 
                      Rise     = c(ifelse(geo_twl[,3]==1, TRUE, FALSE), ifelse(geo_twl[,3]==1, FALSE, TRUE)),
                      Site     = rep(mS$site,2))
twl.rev <- subset(twl.rev, !duplicated(Twilight), sort = Twilight)

grouped <- rep(FALSE, nrow(twl.rev))
grouped[twl.rev$Site>0] <- TRUE 
grouped[c(1:3, (length(grouped)-2):length(grouped))] <- TRUE

# Create a vector which indicates which numbers sites as 111123444444567888889
g <- makeGroups(grouped)

# Add data to twl file
twl$group <- c(g, g[length(g)])


# Add behavior vector
behaviour <- c()
for (i in 1:max(g)){
  behaviour<- c(behaviour, which(g==i)[1])
}
stationary <- grouped[behaviour]
sitenum <- cumsum(stationary==T)
sitenum[stationary==F] <- 0


```



```{r}
x0 <- cbind(tapply(path$x[,1],twl$group,median), 
            tapply(path$x[,2],twl$group,median))


fixedx <- rep_len(FALSE, length.out = nrow(x0))
fixedx[1] <- TRUE
fixedx[c(1, length(fixedx))] <- TRUE

x0[fixedx,1] <- lon.calib
x0[fixedx,2] <- lat.calib

z0 <- trackMidpts(x0)

beta  <- c(1, 0.08)
matplot(0:100, dgamma(0:100, beta[1], beta[2]),
        type = "l", col = "orange",lty = 1,lwd = 2,ylab = "Density", xlab = "km/h")
```



```{r}
earthseaMask <- function(xlim, ylim, n = 2, pacific=FALSE, index) {
  
  if (pacific) {wrld_simpl <- nowrapRecenter(wrld_simpl, avoidGEOS = TRUE)}
  
  # create empty raster with desired resolution
  r = raster(nrows = n * diff(ylim), ncols = n * diff(xlim), xmn = xlim[1],
              xmx = xlim[2], ymn = ylim[1], ymx = ylim[2], crs = proj4string(wrld_simpl))
  
  # create a raster for the stationary period, in this case by giving land a value of 1
  rs = cover(rasterize(elide(wrld_simpl, shift = c(-360, 0)), r, 1, silent = TRUE),
              rasterize(wrld_simpl, r, 1, silent = TRUE), 
              rasterize(elide(wrld_simpl,shift = c(360, 0)), r, 1, silent = TRUE))
  
  # make the movement raster the same resolution as the stationary raster, but allow the bird to go anywhere by giving all cells a value of 1
  rm = rs
  
  # stack the movement and stationary rasters on top of each other
  mask = stack(rs, rm)
  
  xbin = seq(xmin(mask),xmax(mask),length=ncol(mask)+1)
  ybin = seq(ymin(mask),ymax(mask),length=nrow(mask)+1)
  mask = as.array(mask)[nrow(mask):1,,sort(unique(index)),drop=FALSE]

  function(p) mask[cbind(.bincode(p[,2],ybin),.bincode(p[,1],xbin), index)]
}



xlim <- c(100, 130)
ylim <- c(5, 35)

index = ifelse(stationary, 1, 2)

mask <- earthseaMask(xlim, ylim, n = 1, index=index)

## Define the log prior for x and z
logp <- function(p) {
    f <- mask(p)
    ifelse(f | is.na(f), -1000, log(1))
}


```



```{r}
model <- groupedThresholdModel(twl$Twilight,
                               twl$Rise,
                               group = twl$group, #This is the group vector for each time the bird was at a point
                               twilight.model = "ModifiedGamma",
                               alpha = alpha,
                               beta =  beta,
                               x0 = x0, # median point for each group (defined by twl$group)
                               z0 = z0, # middle points between the x0 points
                               zenith = zenith0,
                               logp.x = logp, # land sea mask
                               fixedx = fixedx)


# define the error shape
x.proposal <- mvnorm(S = diag(c(0.005, 0.005)), n = nrow(x0))
z.proposal <- mvnorm(S = diag(c(0.005, 0.005)), n = nrow(z0))

# Fit the model
fit <- estelleMetropolis(model, x.proposal, z.proposal, iters = 1000, thin = 20)
```



```{r}
# use output from last run
x0 <- chainLast(fit$x)
z0 <- chainLast(fit$z)

model <- groupedThresholdModel(twl$Twilight, 
                               twl$Rise, 
                               group = twl$group,
                               twilight.model = "Gamma",
                               alpha = alpha, 
                               beta =  beta,
                               x0 = x0, z0 = z0,
                               logp.x = logp,
                               missing=twl$Missing,
                               zenith = zenith0,
                               fixedx = fixedx)

for (k in 1:3) {
  x.proposal <- mvnorm(chainCov(fit$x), s = 0.3)
  z.proposal <- mvnorm(chainCov(fit$z), s = 0.3)
  fit <- estelleMetropolis(model, x.proposal, z.proposal, x0 = chainLast(fit$x),
                           z0 = chainLast(fit$z), iters = 300, thin = 20)
}

## Check if chains mix
opar <- par(mfrow = c(2, 1), mar = c(3, 5, 2, 1) + 0.1)
matplot(t(fit$x[[1]][!fixedx, 1, ]), type = "l", lty = 1, col = "dodgerblue", ylab = "Lon")
matplot(t(fit$x[[1]][!fixedx, 2, ]), type = "l", lty = 1, col = "firebrick", ylab = "Lat")
par(opar)


x.proposal <- mvnorm(chainCov(fit$x), s = 0.3)
z.proposal <- mvnorm(chainCov(fit$z), s = 0.3)

fit <- estelleMetropolis(model, x.proposal, z.proposal, x0 = chainLast(fit$x),
                         z0 = chainLast(fit$z), iters = 2000, thin = 20, chain = 1)
```



```{r}
# sm <- locationSummary(fit$x, time=fit$model$time)
sm <- SGAT2Movebank(fit$x, time = twl$Twilight, group = twl$group)


colours <- c("black",colorRampPalette(c("blue","yellow","red"))(max(twl.rev$Site)))
data(wrld_simpl)

# empty raster of the extent
r <- raster(nrows = 2 * diff(ylim), ncols = 2 * diff(xlim), xmn = xlim[1]-5,
            xmx = xlim[2]+5, ymn = 5, ymx = 35, crs = proj4string(wrld_simpl))

s <- slices(type = "intermediate", breaks = "week", mcmc = fit, grid = r)
sk <- slice(s, sliceIndices(s))

plot(sk, useRaster = F,col = c("transparent", rev(viridis::viridis(50))), xlim=c(100, 135), ylim=c(0, 90))
plot(wrld_simpl, xlim=c(100, 135), ylim=c(0, 90),add = T, bg = adjustcolor("black",alpha=0.1))

with(sm[sitenum>0,], arrows(`Lon.50.`, `Lat.2.5.`, `Lon.50.`, `Lat.97.5.`, length = 0, lwd = 2.5, col = "firebrick"))
with(sm[sitenum>0,], arrows(`Lon.2.5.`, `Lat.50.`, `Lon.97.5.`, `Lat.50.`, length = 0, lwd = 2.5, col = "firebrick"))
lines(sm[,"Lon.50."], sm[,"Lat.50."], col = "darkorchid4", lwd = 2)

points(sm[,"Lon.50."], sm[,"Lat.50."], pch=21, bg=colours[sitenum+1], 
      cex = ifelse(sitenum>0, 3, 0), col = "firebrick", lwd = 2.5)

points(sm[,"Lon.50."], sm[,"Lat.50."], pch=as.character(sitenum),
       cex = ifelse(sitenum>0, 0.8, 0))



```



```{r}
write.csv(sm, 
          paste0(wd, "SSIN876_SGATGroupSummary.csv"), 
          row.names = F)

save(fit, 
     file = paste0(wd, "SSIN876_SGATGroupfit.RData"), 
     compress = T)
```

